A Kochen-Specker system has at least 21 vectors\\ {\small (extended abstract)}

### 2014-09-08 paper/main.tex
paper: add event; add forward reference

@@

\title{A Kochen-Specker system has at least 21 vectors\\
        {\small (extended abstract)}}
\def\titlerunning{A Kochen-Specker system has at least 21 vectors
            (extended abstract)}
\def\authorrunning{Uijlen \& Westerbaan}

>>>>

\providecommand{\event}{QPL2014}

@@

\title{A Kochen-Specker system has at least 21 vectors\\
        {\small (extended abstract)
            \footnote{This is a condensed version of the article
                        to be published in Ohmsha-Springer's
                        New Generation Computing.
                    One can find a preprint of the full version at
                    \url{http://westerbaan.name/\~bas/math/ks.pdf}}}}
\def\titlerunning{A Kochen-Specker system has at least 21 vectors
            (extended abstract)}
\def\authorrunning{Uijlen \& Westerbaan}
